\subsubsection{Classical solution for \texorpdfstring{$\peclet =
\infty$}{infinite Péclet's number}}

Whenever $\peclet \to +\infty$, it implies $\Gamma \to 0^+$ since infinite
values for the density, velocity or characteristic length make no physical
sense. Therefore the difussion coefficient tends to $0$, which means the
Laplacian term, linked to the diffusion process, is negligible. Dividing the PDE
from \eqref{eq:diagonal_case_cauchy_problem} by Péclet's number results in the
following equation
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_eq1}
	\phi_x + \phi_y = 0 \quad \text{in } \Omega
\end{equation}
The following natural step would be considering equation
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_eq1} with $g$ as boundary
condition on all $\partial \Omega$, that is to say, the following problem:
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_overdetermined_problem}
	\left\{
	\begin{aligned}
		\phi_x + \phi_y &= 0 &
		&\text{in } \Omega \\
		\phi &= g &
		&\text{on } \partial \Omega
	\end{aligned}
	\right.
\end{equation}
Nonetheless, problem
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_overdetermined_problem}
is ``overdetermined'', which means a part of the boundary condition is
unnecessary due to the geometric properties of the PDE as we shall see. In order
to obtain a problem we can solve, take the curve $C = \left( [0,L] \times \{ 0
\} \right) \cup \left( \{ 0 \} \times (0,L] \right)$, and let $\tilde{g} \colon
C \subset \real^2 \rightarrow \real$ be
\begin{equation*}
	\tilde{g}(x,y) = 
	\left\{
	\begin{aligned}
		&\phi_\text{low} 	& &\text{if } (x,y) \in [0,L] \times \{ 0 \} \\
		&\phi_\text{high} 	& &\text{if } (x,y) \in \{ 0 \} \times (0,L] \\
	\end{aligned}
	\right.
\end{equation*}
which is the restriction of $g$ to $C$, that is to say, $\tilde{g} = g
\rvert_C$. The resulting Cauchy problem is
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet}
	\left\{
	\begin{aligned}
		\phi_x + \phi_y &= 0 &
		&\text{in } \Omega \\
		\phi &= \tilde{g} &
		&\text{on } C
	\end{aligned}
	\right.
\end{equation}
The PDE from \eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} is known as
the transport equation, which is a first--order linear PDE. In our case it has
constant coefficients, making it easier to solve analitically.\footnote{Actually
equation \eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} is not the
transport equation, since neither $x$ nor $y$ are time variables but space
variables. The homogeneous transport equation is $u_t + b \vdot \grad{u} = 0$ in
$\real^n \times (0,\infty)$ where $u \colon \real^n \times [0,\infty) \to \real$
is the unknown. The importance of the time variable is that it gives the
``cylinder'' $\real^n \times [0,\infty) \subset \real^{n+1}$ where the equation
occurs. Nonetheless problem
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} takes place in the
domain $(0, L) \times (0, L)$ which is a cylinder as well, hence the $y$
variable can be regarded as a time variable and solve the equation.}

\begin{definition*}
	A classical solution to problem
	\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} is a function $\phi
	\colon \overline{\Omega} \rightarrow \real$ such that:
	\begin{enumerate}[label={(\roman*)}, topsep=0pt]
		\item $\phi \in \mathcal{C}^1(\overline{\Omega})$, \ie $\phi$ is a
		$\mathcal{C}^1(\Omega)$ function that admits a $\mathcal{C}^1$ extension
		to an open neighbourhood of every point in $\partial \Omega$,
		\item $\phi$ satisfies the PDE and
		\item $\phi$ satisfies the boundary conditions.
	\end{enumerate}
\end{definition*}
\noindent
In order to find the solution to
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet}, we will assume $\phi$
is a $\mathcal{C}^1(\overline{\Omega})$ function. Once we find the solution we
will be able to tell whether $\phi$ is a classical solution. Moreover, so as to
find a candidate of solution, we will make some assumptions motivated by
intuiton and with lack of rigour, and later we shall justify them properly. This
is a common practice in PDE theory.

We introduce some notation that will be useful. Given $m$ vectors $\vb{w}_1,
\ldots, \vb{w}_m \in \real^n$, the set $[\vb{w}_1, \ldots, \vb{w}_m] = \{
\sum_{i=1}^m \lambda_i \vb{w}_i \mid \lambda_1, \ldots, \lambda_m \in \real \}$
is the vector subspace of $\real^n$ spanned by $\vb{w}_1, \ldots, \vb{w}_m$. If
$W \subset \real^m$ is a vector subspace, $W^\perp = \{ v \in \real^n \mid v
\vdot w = 0 \ \forall w \in W \}$ is the vector subspace orthogonal to $W$.

The method we will follow to find the solution is known as the method of
characteristics. Using $\grad{\phi}$ we can write the PDE as
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_orthogonal_vectors}
	\left( 1, 1 \right)
	\vdot
	\grad{\phi}(x,y) = 
	\left( 1, 1 \right)
	\vdot
	\begin{pmatrix}
		\phi_x(x,y) \\ \phi_y(x,y)
	\end{pmatrix} = 
	\phi_x(x,y) + \phi_y(x,y) = 0
\end{equation}
Recall from vector calculus that the gradient vector of $\phi$ gives the
direction of maximum growth of $\phi$ at each point, whilst a non--zero vector
$\vb{w} \in [\grad{\phi}(x,y)]^\perp$ provides the direction at $(x,y)$ along
which $\phi$ remains constant. Equation
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_orthogonal_vectors} tells
us that at each point $(x,y) \in \Omega$, $\phi$ is constant along the direction
given by $(1, 1)$. To prove this, we exploit the fact that the PDE is
first--order linear and use the chain rule to rewrite
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_orthogonal_vectors}.
Consider a $\mathcal{C}^1$ mapping $\alpha(s) = (\alpha_1(s), \alpha_2(s))$ such
that $\alpha_1' = \alpha_2' = 1$ for all $s$. Since $\alpha$ is a mapping from
some subset of $\real$ to $\real^2$, its image
\begin{equation*}
	A = 
	\image \alpha = 
	\left\{ (x,y) \in \real^2 \mid x = \alpha_1(s), \ y = \alpha_2(s), \ s \in \real \right\}
\end{equation*}
can be thought of as a $\mathcal{C}^1$ curve. Moreover, we may choose the curve to
pass through $\Omega \cup C$ as we shall see in a moment. The restriction of $\phi$
to $A$, given by the composition $\varphi = \phi \circ \alpha \colon I \subset
\real \rightarrow \real$, is also a $\mathcal{C}^1$ function as it is
composition of $\mathcal{C}^1$ functions. By the chain rule,
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_chain_rule}
	\frac{\dd}{\dd{s}} \varphi(s) = 
	\frac{\dd}{\dd{s}} \phi(\alpha_1(s), \alpha_2(s)) = 
	\phi_x (\alpha_1(s), \alpha_2(s)) \alpha_1'(s) +  	
	\phi_y (\alpha_1(s), \alpha_2(s)) \alpha_2'(s) =
	\phi_x + \phi_y = 0
\end{equation}
where the last equality holds whenever $\alpha(s) \in \Omega$. Equation
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_chain_rule} implies that
$\phi$ is constant on every connected component of $A \cap
\Omega$, thereby proving our claim. 

The following step is to find the curve $A$. Consider the mapping 
\begin{equation*}
	\begin{aligned}
		f \colon \real^3 &\longrightarrow \real^2 \\
		(s,x,y) &\longmapsto f(s,x,y) = (1,1)
	\end{aligned}
\end{equation*}
By taking a point $(x_0, y_0) \in \Omega \cup C$, we can find the curve $A$
passing by $(x_0, y_0)$:
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_problem}
	\left\{
		\begin{aligned}
			&\alpha' = f(s,\alpha) = (1,1) & &\text{in } I \subset \real \\
			&\alpha(0) = (x_0, y_0)
		\end{aligned}
	\right.
\end{equation}
The function $f$ is constant, therefore is Lipschitz continuous on $(x,y)$ and
uniformly with respect to $s$, thus the solution to
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_problem}
exists and is unique due to the Picard--Lindelöf Theorem (Theorem
\ref{teo:picard_lindelof}). In addition, it is given by
\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_solution}
	\alpha(s) = (x_0 + s, y_0 + s) = (x_0, y_0) + s(1, 1) \quad s \in I \subset \real
\end{equation}
whence $A$ is the line passing by $(x_0, y_0)$ with director subspace $[(1,
1)]$. Moreover $A$ is not a single line, but rather a family of lines with
different initial condition. Hereinafter, we will take $(x_0,y_0) \in
C$\footnote{At the points $(x_0,y_0) \in C$ we have the boundary condition, \ie
we have information about the solution $\phi$.}. To distinguish the solutions
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_problem}
we will denote them by $\alpha(s; x_0, y_0)$, and the curves by $A_{(x_0,y_0)}$.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		% Lenghts
		\def\alength{5}
		\def\L{4.5}
		\def\mlength{0.1}
		% Axis
		\draw[-stealth] (0,-0.5) -- (0,\alength) node[right]{$y$};
		\draw[-stealth] (-0.5,0) -- (\alength,0) node[above]{$x$};
		\draw[black, thick] (\L,0) -- ++(0,-\mlength) node[below]{$L$};
		\draw[black, thick] (0,\L) -- ++(-\mlength,0) node[left]{$L$};
		% Domain
		\fill[cyan!70!white,opacity=0.7] (0,0) rectangle (\L, \L);
		\draw[thick, thick] (0,\L) -- (0,0) -- (\L,0);
		% Characteristics
%		\draw[black] (0,0) -- node[midway, above, rotate=45]{\tiny{$x - y = 0$}} (\L, \L);
		\node[blue] at ({0.5*\L}, {0.5*\L}) {$\Omega$};
		\draw[black] (0,0) -- ({0.45*\L}, {0.45*\L});
		\draw[black] ({0.55*\L}, {0.55*\L}) -- (\L, \L);		
		\draw[black] ({0.25*\L}, 0) -- (\L, {0.75*\L});
		\draw[black] ({0.50*\L}, 0) -- (\L, {0.50*\L});
		\draw[black] ({0.75*\L}, 0) -- (\L, {0.25*\L});		
		\draw[black] (0, {0.25*\L}) -- ({0.75*\L}, \L);
		\draw[black] (0, {0.50*\L}) -- ({0.50*\L}, \L);
		\draw[black] (0, {0.75*\L}) -- ({0.25*\L}, \L);
		% Points
		\filldraw[black] (0,{0.75*\L}) circle (1.5pt);
		\filldraw[black] (0,{0.50*\L}) circle (1.5pt);
		\filldraw[black] (0,{0.25*\L}) circle (1.5pt);
		\filldraw[black] (0,0) circle (1.5pt);
		\filldraw[black] ({0.25*\L},0) circle (1.5pt);
		\filldraw[black] ({0.50*\L},0) circle (1.5pt);
		\filldraw[black] ({0.75*\L},0) circle (1.5pt);
		% Text
		\node[black, anchor=east] at (0,{0.75*\L}) {\tiny{$(0,3L/4)$}};
		\node[black, anchor=east] at (0,{0.50*\L}) {\tiny{$(0,L/2)$}};
		\node[black, anchor=east] at (0,{0.25*\L}) {\tiny{$(0,L/4)$}};
		\node[black, anchor=north east] at (0,0) {\tiny{$(0,0)$}};
		\node[black, anchor=north] at ({0.25*\L},0) {\tiny{$(L/4,0)$}};
		\node[black, anchor=north] at ({0.50*\L},0) {\tiny{$(L/2,0)$}};
		\node[black, anchor=north] at ({0.75*\L},0) {\tiny{$(3L/4,0)$}};
	\end{tikzpicture}
	\captionsetup{width=0.70\linewidth}
	\caption{Some of the lines given by
	\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_solution}
	with initial condition $(x_0,y_0) \in C$ extended to the top and right
	boundaries of $\Omega$.}
	\label{fig:diagonal_case_cauchy_problem_infinite_peclet_lines_from_C}
\end{figure}

We claim that a solution
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_solution}
can be extended so that $\alpha(s;x_0,y_0)$ eventually reaches the top or right
boundaries of $\Omega$ as shown in figure
\ref{fig:diagonal_case_cauchy_problem_infinite_peclet_lines_from_C}. Take $T >
0$ and $\delta > 0$ to be some constants to be determined and let $V = [0, T]
\times \overline{B((x_0,y_0), \delta)} \subset \real^3$. Since $f$ is a constant
function, we have
\begin{equation*}
	M = 
	\sup_{(s,x,y) \in V} \norm{f(s,x,y)} = 
	\max_{(s,x,y) \in V} \norm{f(s,x,y)} = 
	\sqrt{2}
\end{equation*} 
Again, by the Picard--Lindelöf theorem, the solution
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_solution}
exists for $s \in I = [0, T_0] \subset \real$ and remains in
$\overline{B((x_0,y_0), \delta)}$ where $T_0 = \min{\left\{ T, \frac{\delta}{M}
\right\}}$. By taking $\delta = \sqrt{2} L$ and $T = L$, applying the theorem we
obtain $T_0 = L$ and the solution stays in $\overline{B((x_0,y_0), \sqrt{2}
L)}$. Since $\sqrt{2} L$ is the maximum of the distances between two points
belonging to $\overline{\Omega}$, we have proved our claim. As a consequence, by
changing $(x_0,y_0)$ we can fill $\overline{\Omega}$ with these curves. All
except one of the solutions $\alpha(s;x_0,y_0)$ actually exit
$\overline{\Omega}$, however we do not care about the part of the curve outside
$\overline{\Omega}$\footnote{We have such freedom to choose the constants $T$
and $\delta$ because $f$ is a constant function.}.

Up to now, we have found out the following:
\begin{enumerate}[label={(\roman*)}, topsep=0pt]
	\item The lines given by $\alpha(s;x_0,y_0)$ can be extended so that both
	ends touch $\partial \Omega$. The implicit form of these is
	\begin{equation} \label{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_implicit_form}
		A_{(x_0,y_0)} \colon x - y = x_0 - y_0, \quad (x_0,y_0) \in C
	\end{equation}
	\item The lines
	\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_implicit_form}
	fill $\overline{\Omega}$.
	\item By equation
	\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_chain_rule}, the
	function $\phi$ is constant on every line
	\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_implicit_form}.
	\label{eq:infinite_peclet_point_2}
\end{enumerate}
The curves
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet_characteristics_implicit_form}
are known as the characteristic lines (or simply characteristics) of problem
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet}. Some of them are
picture in figure
\ref{fig:diagonal_case_cauchy_problem_infinite_peclet_characteristics_problem}.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		% Lenghts
		\def\alength{5}
		\def\L{4.5}
		\def\mlength{0.1}
		% Axis
		\draw[-stealth] (0,-0.5) -- (0,\alength) node[right]{$y$};
		\draw[-stealth] (-0.5,0) -- (\alength,0) node[above]{$x$};
		\draw[black, thick] (\L,0) -- ++(0,-\mlength) node[below]{$L$};
		\draw[black, thick] (0,\L) -- ++(-\mlength,0) node[left]{$L$};
		% Domain
		\fill[cyan!70!white,opacity=0.7] (0,0) rectangle (\L, \L);
		\draw[thick, thick] (0,0) rectangle (\L, \L);
		% Characteristics
%		\draw[black] (0,0) -- node[midway, above, rotate=45]{\tiny{$x - y = 0$}} (\L, \L);
		\node[rotate=45] at ({0.5*\L}, {0.5*\L}) {\tiny{$x - y = 0$}};
		\draw[black] (0,0) -- ({0.4*\L}, {0.4*\L});
		\draw[black] ({0.6*\L}, {0.6*\L}) -- (\L, \L);
		
		\draw[black] ({0.25*\L}, 0) -- node[midway, above, rotate=45]{\tiny{$x - y = L/4$}} 
		(\L, {0.75*\L});
		\draw[black] ({0.50*\L}, 0) -- node[midway, above, rotate=45]{\tiny{$x - y = L/2$}} 
		(\L, {0.50*\L});
		\draw[black] ({0.75*\L}, 0) -- node[midway, above, rotate=45]{\tiny{$x - y = 3L/4$}} 
		(\L, {0.25*\L});
		
		
		
		\draw[black] (0, {0.25*\L}) -- node[midway, below, rotate=45]{\tiny{$x - y = -L/4$}} 
		({0.75*\L}, \L);
		\draw[black] (0, {0.50*\L}) -- node[midway, below, rotate=45]{\tiny{$x - y = -L/2$}} 
		({0.50*\L}, \L);
		\draw[black] (0, {0.75*\L}) -- node[midway, below, rotate=45]{\tiny{$x - y = -3L/4$}} 
		({0.25*\L}, \L);
	\end{tikzpicture}
	\caption{Some characteristics of problem \eqref{eq:diagonal_case_cauchy_problem_infinite_peclet}.}
	\label{fig:diagonal_case_cauchy_problem_infinite_peclet_characteristics_problem}
\end{figure}

We know the value of $\phi$ at $(x_0,y_0) \in C$ and $\phi$ is constant along
the curve $A_{(x_0,y_0)}$. Therefore the value of $\phi$ at $(x,y) \in
A_{(x_0,y_0)}$ is $\phi(x,y) = \phi(x_0,y_0) = \tilde{g}(x_0,y_0)$. As
$(x_0,y_0) \in C$ implies either $x_0 = 0$ or $y_0 = 0$ (or both), we have the following:
\begin{itemize}[topsep=0pt]
	\item If $y \leq x$ then $\phi(x,y) = \phi(x-y,0) = \tilde{g}(x-y,0)$.
	\item If $y > x$ then $\phi(x,y) = \phi(0,y-x) = \tilde{g}(0,y-x)$.
\end{itemize}
With this in mind, the solution to \eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} is:
\begin{equation} \label{eq:diag_inf_pe_solution}
	\phi(x,y) = 
	\left\{
		\begin{aligned}
			&\tilde{g}(x-y,0) = \phi_\text{low} & &\text{if } y \leq x \\
			&\tilde{g}(0,y-x) = \phi_\text{high} & &\text{if } y > x \\
		\end{aligned}
	\right.
	\quad
	(x,y) \in \overline{\Omega}
\end{equation}
Intuitively, the characteristics give the paths in $\real^2$ through which the
information of the boundary conditions is transported. 

After finding the solution, we should check if $\phi \in
\mathcal{C}^1(\overline{\Omega})$. First consider the case when $\phi_\text{low}
= \phi_\text{high}$.

\begin{theorem}
	Assume $\phi_\text{low} = \phi_\text{high}$. Then the solution to problem
	\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} exists and is
	unique. Moreover it is a solution in the classical sense.
\end{theorem}
\begin{proof}
	We have proved the existence of a solution by giving formula
	\eqref{eq:diag_inf_pe_solution}. The uniqueness is a consequence of the
	method of characteristics. In it we have seen that $\phi$ is constant on
	each the characteristic, then we have found the equation of characteristics
	and and proved that given an initial condition $(x_0,y_0) \in C$, the curve
	is unique. Finally $\phi$ is a $\mathcal{C}^1(\Omega) \cap
	\mathcal{C}(\overline{\Omega})$ function because it is constant on
	$\overline{\Omega}$ and clearly satisfies the boundary condition by
	construction and the PDE.
\end{proof}

Assume $\phi_\text{low} < \phi_\text{high}$, then $\phi$ is not continuous on
the segment $\{ x - y = 0 \} \cap \overline{\Omega}$ thus it cannot be a
differentiable function, implying that function \eqref{eq:diag_inf_pe_solution}
is not a classical solution. This could be warned from the beginning, since any
function satisfying the boundary condition of problem
\eqref{eq:diagonal_case_cauchy_problem_infinite_peclet} is not continuous at
$(0,0)$.

