
\subsection{Analytical solution}

Before going into the properties and the analytical solution to certain
boundary--value problems related to the diagonal flow case, a question that
arises naturally is the following: why shall we bother about the properties of a
problem analytically when we can solve it numerically? There exists two reasons:
\begin{itemize}
	\item The properties of a certain partial differential equation dictate what
	computational methods are suitable to solve it. For instance, consider
	\begin{equation} \label{eq:heat_problem_example}
		\begin{aligned}
			\left\{
				\begin{aligned}
					u_t - u_{xx} &= 0 & &\text{in } \real \times (0,\infty) \\
					u &= g & &\text{on } \real \times \{ t = 0 \}
				\end{aligned}
			\right.
		\end{aligned}
	\end{equation}
	\begin{equation} \label{eq:wave_problem_example}
		\begin{aligned}
			\left\{
				\begin{aligned}
					u_{tt} - u_{xx} &= 0 & &\text{in } \real \times \real \\
					u &= d & &\text{on } \real \times \{ t = 0 \} \\
					u_t &= h & &\text{on } \real \times \{ t = 0 \}
				\end{aligned}
			\right.
		\end{aligned}
	\end{equation}
	where $g, d, h \colon \real \to \real$ are given functions and $u = u(x,t)$
	is the unknown. Problems \eqref{eq:heat_problem_example} and
	\eqref{eq:wave_problem_example} are the typical diffusion problem and wave
	equation problem on the real line. If $g$ is a continuous function, it is
	widely known that the solution to \eqref{eq:heat_problem_example} is a
	$\mathcal{C}^\infty(\real \times (0,\infty))$, but in general it is only
	defined for positive times. Therefore the diffusion equation has a
	regularizing effect on the initial condition $g$. Now assume $d \in
	\mathcal{C}^2(\real)$ and $h \in \mathcal{C}^1(\real)$. Then the solution to
	\eqref{eq:wave_problem_example} is a $\mathcal{C}^2(\real \times \real)$,
	hence the wave equation does no make the initial conditions smoother, but is
	defined both for positive and negative times. Intuitively, the enormous
	differences between the properties of problems
	\eqref{eq:heat_problem_example} and \eqref{eq:wave_problem_example} should
	warn that different numerical methods should be used to solve them.
	
	\item Boundary--value problems and initial--value problems which are not
	well--posed might have more than one solution in a certain sense that must
	be specified. Hence if a problem with no unique solution is solved
	numerically, it is uncertain what solution is obtained and whether it has
	physical meaning.
\end{itemize}

As we have previously seen, Péclet's number is defined as
\begin{equation*}
	\peclet = 
	\frac{\text{convection transport rate}}{\text{diffusion transport rate}} = 
	\frac{\rho v_0 L}{\Gamma}
\end{equation*}
Note that the factor $\beta$ in the PDE from problem
\eqref{eq:diagonal_case_cauchy_problem} is a constant determined by the
geometry, whereas Peclet's number depends on the fluid and on the velocity
field. Since no more factors intervene on the PDE, this tells us that the
behaviour of the solution will depend greatly on Peclet's number. 

\input{sections/case_diagonal_flow/analytical_solution/Pe_inf_classical.tex}
% \input{sections/case_diagonal_flow/analytical_solution/Pe_inf_weak.tex}
\input{sections/case_diagonal_flow/analytical_solution/Pe_fin_classical.tex}
\input{sections/case_diagonal_flow/analytical_solution/Pe_fin_weak.tex}

