\subsubsection{Classical solution for \texorpdfstring{$\rho / \Gamma =
\infty$}{infinite rho/Gamma quotient}}

We assume $L = 1 \ \meter$. As in the diagonal case, when $\rho / \Gamma =
\infty$ we have $\peclet = \infty$. Dividing the PDE by Péclet's number results
in the following transport problem:
\begin{equation} \label{eq:smith_hutton_cauchy_problem_infinite_peclet_0} 
	\left\{
	\begin{aligned}
		u(x,y) \phi_x + v(x,y) \phi_y &= 0 	& &\text{in } \Omega \\
		\phi &= g 							& &\text{on } C_1 \cup C_2 \\
		\phi_y &= 0 						& &\text{on } C_3
	\end{aligned}
	\right.
\end{equation}
However, problem \eqref{eq:smith_hutton_cauchy_problem_infinite_peclet_0} is
overdetermined due to Neumann's boundary condition on $C_3$, thus we shall consider problem
\begin{equation} \label{eq:smith_hutton_cauchy_problem_infinite_peclet} 
	\left\{
	\begin{aligned}
		u(x,y) \phi_x + v(x,y) \phi_y &= 0 	& &\text{in } \Omega \\
		\phi &= g 							& &\text{on } C_1 \cup C_2
	\end{aligned}
	\right.
\end{equation}

In order to give a solution to
\eqref{eq:smith_hutton_cauchy_problem_infinite_peclet} we will follow the method
of characteristics again. Take $(x_0, y_0) \in \overline{\Omega}$ and consider a
$\mathcal{C}^1$ mapping $\alpha(s) = (x(s), y(s))$ such that
\begin{equation} \label{eq:smith_hutton_characteristics}
	\left\{
		\begin{aligned}
			x' &= u(\alpha(s)) = 2 y (1 - x^2) 		& &x(0) = x_0 \\
			y' &= v(\alpha(s)) = - 2 x (1 - y^2) 	& &y(0) = y_0 \\
		\end{aligned}
	\right.
\end{equation}
Consider the composition $h = \phi \circ \alpha$, which is well defined as long
as $\alpha(s) \in \Omega$. Then
\begin{multline*}
	\frac{\dd}{\dd{s}} h(s) = 
	\frac{\dd}{\dd{s}} \phi(x(s), y(s)) = 
	\phi_x(x(s), y(s)) x'(s) + \phi_y(x(s), y(s)) y'(s) \\ =
	\phi_x(x(s), y(s)) u(x(s), y(s)) + 
	\phi_y(x(s), y(s)) v(x(s), y(s)) = 0
\end{multline*}
thus $\phi$ is constant on the curve given by $\alpha$. Problems
\eqref{eq:vel_smith_hutton_ivp} and \eqref{eq:smith_hutton_characteristics} are
the same, hence the characteristics and streamlines are the same curves.
Applying proposition \eqref{prop:existence_uniqueness_streamlines}, the
characteristic passing through $(x_0, y_0) \in \overline{\Omega}$ exists and is
unique. As a result, two characteristic curves cannot intersect each other. In
order to distinguish characteristics, we shall denote them by
$\alpha(s;x_0,y_0)$. 

So as to know the interval $I \subset \real$ where the solution
$\alpha(s;x_0,y_0)$ is defined, we have the following proposition which relies
on theorem \ref{teo:picard_lindelof}.

\begin{prop} \label{prop:characteristics_extension}
	The characteristic curve $\alpha(s;x_0,y_0)$ can be extended as
	long as $\alpha(s;x_0,y_0) \in \overline{\Omega}$.
\end{prop}
\begin{proof}
	Let $T > 0$ be a constant to be determined and consider the sets $U = [-2T,
	2T] \times B((0,0), 5)$ and $V(x_0,y_0) = [0,T] \times
	\overline{B((x_0,y_0), 3)}$. Observe that $V(x_0,y_0) \subsetneq U$ for all
	$(x_0,y_0) \in \overline{\Omega}$. Since $f \in \mathcal{C}(\real^3)$, we
	have $\norm{f} \in \mathcal{C}(\real^3)$, which implies $\norm{f} \in
	\mathcal{C}(\overline{U})$. Moreover $\overline{U}$ is compact so $\norm{f}$
	reaches a maximum on it that satisfies
	\[
	\sup_{(t,x,y) \in V(x_0,y_0)} \norm{f} \leq
	\sup_{(t,x,y) \in \overline{U}} \norm{f} = 
	\max_{(t,x,y) \in \overline{U}} \norm{f} = M	
	\]
	and serves as upper bound for all $V(x_0,y_0)$. Now take $T = \frac{3}{M}$.
	By applying the Picard--Lindelöf theorem, we find that the solution exists
	for $t \in \tilde{I} = [-\frac{3}{M}, \frac{3}{M}]$ and stays in
	$\overline{B((x_0,y_0), 3)}$. Note that the maximum of the distances between
	two points in $\overline{\Omega}$ is $\sqrt{5}$, thus $\overline{\Omega}
	\subsetneq \overline{B((x_0,y_0), 3)}$ for any $(x_0,y_0) \in
	\overline{\Omega}$. Now we ask whether the characteristic has exited
	$\overline{\Omega}$ or not. If the characteristic has exited
	$\overline{\Omega}$ then we stop extending it. Otherwise let $(\tilde{x}_0,
	\tilde{y}_0) = \alpha(3/M; x_0, y_0)$ and consider the initial value problem
	\[
		\left\{
			\begin{aligned}
				x' &= u(\alpha(s)) = 2 y (1 - x^2) 		& &x(0) = \tilde{x}_0 \\
				y' &= v(\alpha(s)) = - 2 x (1 - y^2) 	& &y(0) = \tilde{y}_0 \\
			\end{aligned}
		\right.
	\]
	Using the same argument above, we can extend the characteristic as desired.
	The several curves that form the characteristic are $\mathcal{C}^1$ curves
	and agree (both $\alpha$ and $\alpha'$) at the point where they meet, hence
	the characteristic is a $\mathcal{C}^1$ curve and its parametrization is
	defined on an interval $I \subset \real$.
\end{proof}

\noindent
Finally the following proposition characterizes all the characteristic curves
depending on $(x_0, y_0) \in \Omega$.

\begin{prop}
	Consider the initial value problem \eqref{eq:smith_hutton_characteristics}, then:
	\begin{enumerateprop}
		\item If $(x_0, y_0) \in \{ (0,0), \, (-1,1), \, (1,1) \}$, then
		$\alpha$ is a constant mapping.
		\item If $x_0 = -1$ and $y_0 \in [0, 1)$, then the image of $\alpha$ is
		the curve $\{ - 1 \} \times [0, 1)$ and $y$ is a
		strictly increasing function.
		\item If $x_0 = 1$ and  $y_0 \in [0,1)$, then the image of $\alpha$ is
		the curve $\{ 1 \} \times [0, 1)$ and $y$ is a strictly
		decreasing function.
		\item If $x_0 \in (-1,1)$ and $y_0 = 1$, then the image of $\alpha$ is
		the curve $(-1,1) \times \{ 1 \}$ and $x$ is a strictly increasing function.
		\item If $(x_0,y_0) \in \Omega$, the characteristic can be extended so
		that the left end touches $(-1,0) \times \{ 0 \}$ and the right end touches $(0,1) \times \{ 0 \}$.
	\end{enumerateprop}
\end{prop}
\begin{proof}
	We will use extensively the following formula given by proposition \ref{eq:ode_general_formula}
	\begin{equation*}
		\alpha(s) = \alpha(0) + \int_0^s \alpha'(r) \dd{r}, \quad s \in I
	\end{equation*}
	or equivalently
	\begin{equation*}
		\left\{
			\begin{aligned}
				x(s) &= x(0) + \int_0^s x'(r) \dd{r} = 
				x(0) + \int_0^s u(\alpha(r)) \dd{r} \\
				y(s) &= y(0) + \int_0^s y'(r) \dd{r} = 
				x(0) + \int_0^s v(\alpha(r)) \dd{r}
			\end{aligned}
			\quad \text{for } s \in I \\
		\right.
	\end{equation*}
	where $I \subset \real$ is the interval given by proposition
	\ref{prop:characteristics_extension}. We prove each point separately:
	\begin{enumerateprop}
		\item At every point we have $u = v = 0$, therefore the unique solution
		to \eqref{eq:smith_hutton_characteristics} is $\alpha(s) = (x_0, y_0)$
		for all $s \in I$.
		\item We have $u = 0$ and $v > 0$ for each $y_0 \in [0,1)$ and $x_0 =
		-1$. Therefore $x(s) = -1$ 
	\end{enumerateprop}
\end{proof}


We shall follow the method of characteristics again in
order to give a solution of problem
\eqref{eq:smith_hutton_cauchy_problem_infinite_peclet}. However, we will be less
rigorous and we will not check the boundary conditions nor the uniqueness. Let
$I \subset \real$ be an open interval and let $h \colon I \subset \real \to
\real^2$, $s \mapsto h(s) = (x(s), y(s))$ be a mapping satisfying the following:
\begin{equation} \label{eq:smith_hutton_cauchy_problem_infinite_peclet_characteristics_1} 
	\left\{
	\begin{aligned}
		x'(s) &= u(x(s), y(s)) = 2 y (1 - x^2) \\
		y'(s) &= v(x(s), y(s)) = - 2 x (1 - y^2)
	\end{aligned}
	\right.
\end{equation}
Notice that
\eqref{eq:smith_hutton_cauchy_problem_infinite_peclet_characteristics_1} is the
same ODE system as \eqref{eq:velocity_smith_hutton_odes}, which implies the
curves satisfying
\eqref{eq:smith_hutton_cauchy_problem_infinite_peclet_characteristics_1} are
streamlines. Hereinafter, we will use the terms streamline and characteristic as
synonyms. We claim we already know all the characteristics in $\Omega$. Indeed,
we have the following facts:
\begin{enumerate}[label={(\roman*)}, topsep=0pt]
\label{lab:smith_hutton_cauchy_problem_infinite_peclet_i}
	\item When $x = \pm 1$ we have $u(\pm 1, y) = 0$ for all $y \in (0, 1)$
	(there is only $y$--component of velocity).
	\label{lab:smith_hutton_cauchy_problem_infinite_peclet_x}
	\item When $y = 1$ we have $v(x, 1) = 0$ for all $x \in (-1,1)$ (there is
	only $x$--component of velocity).
	\label{lab:smith_hutton_cauchy_problem_infinite_peclet_y}
	\item When $y = 0$ we have $u(x,0) = 0$ for all $x \in (-1,1)$ and the
	$y$--component vanishes nowhere expect at $(0,0)$, but this point does not
	belong to $\Omega$.
	\label{lab:smith_hutton_cauchy_problem_infinite_peclet_iv}
	\item Any two streamlines cannot cross each other. Each point in $\Omega$
	belongs to a single streamline.
	\label{lab:smith_hutton_cauchy_problem_infinite_peclet_v}
	\item The velocity field is non--zero at each point of $\Omega$.
\end{enumerate}
Facts \ref{lab:smith_hutton_cauchy_problem_infinite_peclet_x},
\ref{lab:smith_hutton_cauchy_problem_infinite_peclet_y} and
\ref{lab:smith_hutton_cauchy_problem_infinite_peclet_v} imply that the
characteristic curves cannot exit $\Omega$ through the curve
$C_2 = \left( \{ -L \} \times (0,L) \right) \cup \left( [-L,L] \times \{ L \}
\right) \cup \left( \{ L \} \times [0,L) \right)$. Fact
\ref{lab:smith_hutton_cauchy_problem_infinite_peclet_iv} means that the
velocity field ``pushes upwards'' on the curve $(-1,1) \times \{ 0 \}$, so
characteristics cannot exit $\Omega$ through it either. Finally, fact
\ref{lab:smith_hutton_cauchy_problem_infinite_peclet_y} implies that any two
streamlines cannot die at the same point. Because all streamlines are contained
in $\Omega$ and through each point passes a single streamlines, all
characteristics begin at some point in $(-1,0) \times \{ 0 \}$ and finish at
some point in $(0,1) \times \{ 0 \}$. At $(0,0)$ there is no characteristic
starting or ending since the velocity field vanishes there. As a result, the
initial value problem for characteristics is given by
\eqref{eq:vel_smith_hutton_ivp}, whose existence and uniqueness of solution
we have already proved. 

Until now, we have taken points in the segment $(-1,1) \times \{ 0 \}$ although
these do not belong to $\Omega$. Now we shall formalize this. Since the
characteristics are solutions to the initial value problem
\eqref{eq:vel_smith_hutton_ivp}, these must be at least $\mathcal{C}^1$
curves in $\real^2$, hence must be continuous functions that admit a continuous
extension to the segment $(-1,1) \times \{ 0 \}$.

Finally we find the solution to the transport problem. Consider the function
$\varphi = \phi \circ h \colon I \subset \real \to \real$. By the chain rule we
have
\begin{multline*}
	\frac{\dd}{\dd{s}} \varphi(s) = 
	\frac{\dd}{\dd{s}} \phi(x(s), y(s)) = 
	\frac{\partial \phi}{\partial x} (x(s), y(s)) \, x'(s) + 
	\frac{\partial \phi}{\partial y} (x(s), y(s)) \, y'(s) = \\ =
	u(x(s),y(s)) \frac{\partial \phi}{\partial x} + 
	v(x(s),y(s)) \frac{\partial \phi}{\partial y} = 0
\end{multline*}
where the last equality is true because of the PDE. This means, as we already
know, that the restriction of $\phi$ to the characteristics is a constant
function. Recall that the value of $\phi$ at the boundary segment $(-1,0) \times
\{ 0 \}$ is given by $g$. If $C \subset \Omega$ is a characteristic, then the
value of $\phi$ at each point $(x,y) \in C$ must the value that $g$ takes at the
point of $(-1,0) \cup \{ 0 \}$ that $C$ intersects. In order to give an explicit
form of the solution, we shall define a new function. Let $p = (x,y) \in \Omega$
and let $C \subset \Omega \cup ((-1,0) \times \{ 0 \})$ be the only
characteristic containing $p$. Let $q \in ((-1,0) \times \{ 0 \})$ be the only
point contained in the intersection $C \cap ((-1,0) \times \{ 0 \})$. We define
the following mapping:
\begin{equation*}
	\begin{aligned}
		\alpha \colon \Omega \subset \real^2 &\longrightarrow \real^2 \\
		p &\longmapsto \alpha(p) = q
	\end{aligned}
\end{equation*}
The mapping $\alpha$ takes any point in $\Omega$ and applies it into the only
point contained in the intersection of the characteristic $C$ containing $p$ and
the segment $(-1,0) \times \{ 0 \}$. Intuitively, two nearby points $p_1, p_2
\in \Omega$ are contained in two characteristics $C_1, C_2$ that are close, so
the image of $p_1, p_2$ by $\alpha$ are two nearby points as well. It could be
argued that $\alpha$ is also a $\mathcal{C}^1$ mapping. A possible solution to
the problem \eqref{eq:smith_hutton_cauchy_problem_infinite_peclet} is given by
\begin{equation*}
	\phi(x,y) = 
	\left\{
	\begin{aligned}
		&(g \circ \alpha)(x,y) & &\text{if} (x,y) \in \overline{\Omega} \setminus (C_1 \cup C_2) \\
		&g(x,y) & &\text{otherwise}
	\end{aligned}
	\right.
	\quad (x,y) \in \overline{\Omega}
\end{equation*}

\begin{theorem}
	If a classical solution exists, then it is unique.
\end{theorem}